Applying Multi-Core Model Checking to Hardware-Software Partitioning in Embedded Systems

### 2015-08-24 Docs/Paper/LaTex/template.tex
review experimental evaluation

\begin{itemize}
\item{\textbf{ESBMC: }\textcolor{Red}{
This strategy uses only one core to solve the partitioning problem, it is described in the section 2.3.}}
\item{\textbf{ESBMC MC:  }\textcolor{Red}{
Uses a sequential strategy \{1\:,2\:,\:...\:, \:Hmax\} , there is not parallel controller in this approach, it is described in the section 5.1.}}
\item{\textbf{ESBMC PS:  }\textcolor{Red}{
This approach is similar with ESBMC MC, however it uses a more optimized way to launch the ESBMC instances, it is described in the section 5.2.}}
\item{\textbf{ESBMC PB:  }\textcolor{Red}{
The binary approach uses a parallel binary search, it is described in the section 5.2.}}
\end{itemize}

\textcolor{red}{There is no single tool for solving all benchmarks efficiently. In particular, Vz solves $4$ out of $7$ benchmarks, in the worst case, vZ was more fast than ILP 3.33 times (Patricia code),vZ returned two TO (time outs) in Fuzzy and Mars.}

@@

Table~\ref{experimental-results-matlab-vz-esbmc} shows the experimental results using vZ, Matlab (ILP and GA), and ESBMC (ESBMC\hyp{}MC, ESBMC\hyp{}PS, ESBMC-PB) tools.

>>>>

\begin{itemize}
\item{\textbf{ESBMC:} This strategy uses only one core to solve the partitioning problem, as described in Section~\ref{Verification-Algorithm-using-ESBMC}.
\item{\textbf{ESBMC-MC:} This uses a sequential strategy $\left\{1,2,\ldots, H_{max}\right\}$; there is no parallel controller in this approach, as described in Section~\ref{Multi-core-ESBMC-with-OpenMP}.}
\item{\textbf{ESBMC-PS:} This approach is similar to ESBMC MC; however, it uses a more optimized way to launch the ESBMC instances, as described Section~\ref{Multi-core-ESBMC-with-OpenMP-using-Binary-Search}.}
\item{\textbf{ESBMC-PB:} This strategy uses a parallel binary search, as described in Section~\ref{Multi-core-ESBMC-with-OpenMP-using-Binary-Search}.}}
\end{itemize}

There is no single tool for solving all benchmarks efficiently. In particular, Vz solves $4$ out of $7$ benchmarks, but it does not find the optimal solution for the RC$6$ benchmark; \textcolor{blue}{Nao entendi nada desta frase... the slowest result compared with ILP was Patricia that was 3.33 times faster, vZ returned two TO (time outs) in Fuzzy and Mars.}

@@

Table~\ref{experimental-results-matlab-vz-esbmc} shows the experimental results using vZ, Matlab (ILP and GA), and ESBMC (ESBMC-MC, ESBMC-PS, ESBMC-PB) tools.
